Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-08-07 cosmic_voids.tex
References of different void-finding schemes

On the theoretical side, early descriptions of the evolution of the 
large-scale Universe based on gravitational instabilities in primordial 
stages and leaded by the seminal work of \citet{Zeldovich70}, are highly 
consistent with the Cosmic Web picture, where planar pancake-like regions 
of matter enclose enormous sub-dense voids and are bordered, in turn, by 
thin filaments and high-density clumpy knots. First theoretical models for 
describing formation, dynamics and properties of voids \citep{Hoffman82, 
Icke84, Bertschinger85, Blumenthal92} were dramatically complemented and 
extended by first numerical studies based on simulations \citep{Martel90, 
Regos91, Weygaert93, Dubinski93}. This tendency of using numerical data 
from N-body simulations, fuelled by last generation computing systems and
ever more efficient numerical algorithms, has become increasingly common 
in the last years as a powerful analysis toolkit of cosmic voids (for an 
extensive compilation of previous numerical works, see \citet{Colberg08}).

At present, studying voids may be considered as a threefold enterprise: 
first, they are a key ingredient of the Cosmic Web as they dominate almost 
the entire volume distribution at large-scales and additionally, they 
compensate over-density structures in the total budget of matter. This 
implies that a full understanding of their dynamics and properties is 
essential for fathoming the high complexity of the Cosmic Web. Second, 
they provide a valuable resource for inferring and probing cosmological 
parameters as their structure and dynamics are highly determined by these 
values. Third, they constitute and unique and still largely pristine 
environment in which can be tested and probed theories of galaxy formation 
and evolution.

>>>>

On the theoretical side, early descriptions of the evolution of the 
large-scale Universe, based on gravitational instabilities in primordial 
stages and leaded by the seminal work of \citet{Zeldovich70}, are highly 
consistent with the Cosmic Web picture, where planar pancake-like regions 
of matter enclose enormous sub-dense voids and are bordered, in turn, by 
thin filaments and high-density clumpy knots \citep{Bond96}. First 
theoretical models for describing formation, dynamics and properties of 
voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were 
dramatically complemented and extended by first numerical studies based 
on simulations \citep{Martel90, Regos91, Weygaert93, Dubinski93}. This 
tendency of using numerical data from N-body simulations, fuelled by last 
generation computing systems and ever more efficient numerical algorithms, 
has become increasingly common in the last years as a powerful analysis 
toolkit of cosmic voids (for an extensive compilation of previous 
numerical works, see \citet{Colberg08}).

At present, studying voids may be considered as a threefold enterprise
\citep{Platen07}: first, they are a key ingredient of the Cosmic Web as 
they dominate almost the entire volume distribution at large-scales and 
additionally, they compensate over-dense structures in the total budget of 
matter. This implies that a full understanding of their evolution and 
properties is essential for fathoming the high complexity of the Cosmic 
Web. Second, they provide a valuable resource for inferring and probing 
cosmological parameters as their structure and dynamics are highly 
determined by these values. Third, they constitute and unique and still 
largely pristine environment in which can be tested and probed theories 
of galaxy formation and evolution.

Although a visual recognition of voids on galaxy surveys and simulations
is possible in most cases, a formal systematic identification of them 
is necessary for statistically meaningful studies. However, a basic yet 
essential issue remains regarding the definition itself of what a void is. 
There is not a general consensus about an unambiguous definition of cosmic 
voids and therefore, there can be found many different void finding 
techniques throughout the literature (for a detailed comparison of 
different schemes, see the Void Finder Comparison Project 
\citet{Colberg08}). In spite of the diversity of existing schemes, they 
can be roughly classified into two main types: first, schemes based on 
spatial or redshift distribution of galaxies in surveys or catalogues of 
dark matter halos in simulations \citep{Kauffmann91, Muller00, Gottlober03,
Hoyle04, Brunino07, Foster09, Micheletti14, Sutter14}, and second, schemes 
based on the smooth and continuous matter density field either from 
simulations or reconstruction procedures on surveys \citep{Plionis02, 
Colberg05, Shandarin06, Platen07, Neyrinck08, Neyrinck13, Ricciardelli2013}
